---
title: "Branding vs Deals"
output: pdf_document
---


```{r echo=FALSE, results='hide', cache=TRUE}
setwd("C:/Users/enrique.balp/Desktop/TV_campaign_linio/TV_analysis")
source("./run_analysis.R" )
```

### Country is:
```{r echo=FALSE}
country
```
Mexico

```{r echo=FALSE}
library(ggplot2)

beg1<-as.POSIXlt("20140910",format="%Y%m%d")
end1<-as.POSIXlt("20140916",format="%Y%m%d")

beg2<-as.POSIXlt("20140917",format="%Y%m%d")
end2<-as.POSIXlt("20140923",format="%Y%m%d")

spts1 <- spot[which(as.POSIXlt(spot$tmstmp)>=beg1 & as.POSIXlt(spot$tmstmp)<=end1),]
spts2 <- spot[which(as.POSIXlt(spot$tmstmp)>=beg2 & as.POSIXlt(spot$tmstmp)<=(end2)),]

spts1$type <- "30' Branding"
spts2$type <- "10' Deals"

spts <- rbind(spts1,spts2)
spts$type <- factor(spts$type)
spts$duration <- factor(spts$duration)

glr <- ggplot(spts,aes(y = lift_v, x = rating, colour=type, shape=type)) +
  geom_point() + geom_smooth(method="lm", fill=NA)+ggtitle(paste("Response vs Rating by campaign --",country))

glc <- ggplot(spts,aes(y = lift_v, x = cost, colour=type, shape=type)) +
  geom_point() + geom_smooth(method="lm", fill=NA)+ggtitle(paste("Response vs Cost by campaign --",country))

gcr <- ggplot(spts,aes(y = rating, x = cost, colour=type, shape=type)) +  geom_point() + geom_smooth(method="lm", fill=NA)+ggtitle(paste("Rating vs Cost by Campaign --",country))

########################

gdeals <- ggplot(spts2,aes(y = lift_v, x = rating, colour = factor(date), shape=factor(date))) +
  geom_point() + geom_smooth(method="lm", fill=NA)+ggtitle(paste("Response vs rating by date",country))
```

## Lift in visits VS rating

In the case of Mexico, it seems that the 30" Branding campaing had a higher response per trp point compared to 10" Deals (p=0.018 which means it is a significant difference).

```{r, echo=FALSE, fig.width=6, fig.height=4}
glr
summary(lm(lift_v~rating+type,data=spts))
```
\pagebreak

## Lift in visits VS cost

In Mexico, there is no discernible efficiency difference between Deals and Branding. 

```{r, echo=FALSE, fig.width=6, fig.height=4}
glc
summary(lm(lift_v~cost+type,data=spts))
```
\pagebreak

## Rating VS cost

Because of lower duration, TRPs are cheaper for the 10" spots in a ratio of C10 = 1.25/3 C30

```{r, echo=FALSE, fig.width=6, fig.height=4}
gcr
summary(lm(rating~cost+type,data=spts))
```

\pagebreak

## Deals comparison

Deals were not significantly different in their responses

```{r, echo=FALSE, fig.width=6, fig.height=4}
gdeals
summary(lm(lift_v~rating+date,data=spts))
```
